Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-08 paper/ms.tex
update manuscript

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.3\,{\rm d}$) and roughly
  Jupiter-sized.  Combining the photometry with a prior on the stellar
  parameters derived from the cluster color-magnitude diagram, we find
  that the transits are grazing with $b=0.951\pm0.012$ and $R_{\rm p}
  = 0.77 \pm 0.07 \,R_{\rm Jup}$.  From radial velocity monitoring, we
  limit the minimum mass to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).
  Grazing transits are a cause for concern, as they are usually
  indicative of astrophysical false positive scenarios.  Our follow-up
  data show that such scenarios are highly unlikely.  Our combined
  multi-color photometry, high-resolution imaging, and radial
  velocities rule out hierarchical eclipsing binary scenarios.
  Background eclipsing binary scenarios, though limited by speckle
  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
  therefore a validated adolescent exoplanet.  Further observations of
  its stellar obliquity, atmosphere, and mass should confirm its
  planetary nature beyond doubt, and could improve our understanding
  of how the physical and orbital properties of exoplanets change in
  time.
\end{abstract}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} The 3$^{\rm rd}$ and 97$^{\rm
    th}$ percentiles in the planet-to-star size ratio correspond to
    planet sizes $0.65\,R_{\rm Jup}$ and $0.91\,R_{\rm Jup}$.  This
    plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

>>>>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore $35^{+11}_{-5}$ million
  years old.  The planet is warm ($P = 8.3\,{\rm d}$) and slightly
  smaller than Jupiter.  Combining the photometry with a prior on the
  stellar parameters derived from the cluster color-magnitude diagram,
  we find that the transits are grazing with $b=0.951\pm0.012$ and
  $R_{\rm p} = 0.77 \pm 0.07 \,R_{\rm Jup}$.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as
  they are usually indicative of astrophysical false positive
  scenarios.  Our follow-up data show that such scenarios are highly
  unlikely.  Our combined multi-color photometry, high-resolution
  imaging, and radial velocities rule out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios, though
  limited by speckle imaging, formally remain a 0.2\% possibility.
  TOI 837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} The  planet-to-star size ratio
    corresponds to a planet size between $0.65\,R_{\rm Jup}$ and
    $0.91\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
    This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}
